Insert the article title here

### 2020-07-23 tex/background.tex

>>>>

\medskip

Reproducibility and replication (we could call it R\&R), on the other hand, preoccupy scientific communities more recently. 
Agreement on the terminology, to begin with, has been elusive \cite{barba2018}. 
The National Academies of Science, Engineering and Medicine (NASEM) released in May 2019 a consensus study report on Replicability and Reproducibility in Science \cite{NASEM2019} with definitions as follows.
``Reproducibility is obtaining consistent results using the same input data, computational steps, methods, and code, and conditions of analysis.
Replicability is obtaining consistent measurements or results, or drawing consistent conclusions using new data, methods, or conditions, in a study aimed at the same scientific question.''
According to these definitions, reproducibility demands full transparency of the computational workflow, which at the very least means open code and open data?where `open` means shared at time of publication (or earlier) under a standard public license. 
This condition is hardly common: among the few systematic efforts to assess the state of reproducibility that have been made, more than half of surveyed works cannot be reproduced, mainly due to missing digital artifacts.
